---
"Mobile elements identification"
---
The mobile elements were identified in several steps according to their classes:

1.- Genomic and pathogenic islands
2.- Integrons
3.- Prophages
4.- CRISPR

1.- Genomic and pathogenic islands.

Genomic and pathogenic islands were predicted online with the server [IslandViewer 3](http://www.pathogenomics.sfu.ca/islandviewer/upload/)

2.- Integrons
Integrons were predicted with [Integron Finder](https://github.com/gem-pasteur/Integron_Finder)
  
```{r,eval=FALSE}
bash Predict_integrons.sh
```

The presence of each type of integron was retrieved for each genome
```{r,eval=FALSE}
bash get_data_integron.sh
```

3.- Prophages

Prophages were predicted with the [PHASTER](http://phaster.ca/) server through their URL API.

Each genome was uploaded as:
```{r,eval=FALSE}
for i in $(ls *.fasta); do wget --post-file="$i" "http://phaster.ca/phaster_api" -O $i.phaster; done
```

The ID for each submission was extracted as follow:
```{r,eval=FALSE}
for i in $(ls *.phaster); do
	ID="$(sed -e 's/,/\t/g' $i | sed 's/\"//g' | sed -e 's/:/\t/g' | cut -f2)"
	sed -e 's/,/\t/g' $i | sed 's/\"//g' | sed -e 's/:/\t/g' | cut -f2 >> ID_list
	echo "wget \"http://phaster.ca/phaster_api?acc="$ID\"" -O "$i"_new"
done

```

After the files were processed, we downloaded the results:

```{r,eval=FALSE}
input="ID_list"
while IFS='' read -r ids || [[ -n "$ids" ]]; do
	wget -O $ids.phaster  "http://phaster.ca/jobs/$ids/summary.txt"
done < "$input"

```

Each result file was manually renamed in order to match the name of its genome. For each genome, we extract the number or intact prophages

```{r,eval=FALSE}
for i in $(*.fasta.phaster); do grep "intact prophage" $i >>number_phages; done
```


3.- CRISPR

CRISPR sequences were identified with the [CRISPR Recognition Tool](http://www.room220.com/crt/)
```{r,eval=FALSE}
for i in $(ls *.fasta); do java -cp  CRT1.2-CLI.jar crt $i; done
```

